---
title: "Homework 1"
author: "Wenxin Tian"
date: "`r Sys.Date()`"
output: github_document
---

# Problem 1:

1. Importing data:

```{r, echo = FALSE, message = FALSE}
library(moderndive)
library(tidyverse)
```

```{r}
data("early_january_weather")
```

2. A glimpse at the data:

```{r}
head(early_january_weather)
```


3. Short description of the data:

The imported data consists of weather conditions taken in early January in 2013. 
The variables include `r colnames(early_january_weather)`. The dataset has a size of 
`r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns, which means 
the data has `r ncol(early_january_weather)` variables taken across `r nrow(early_january_weather)`
 different timepoints. Across all the timepoints, the main temperature was `r round(mean(pull(early_january_weather, temp)), digits = 2)`
  degrees.
  
4. Scatter plot showing temperature and humidity across different hours:

```{r}
ggplot(
  early_january_weather, 
  aes(x = time_hour, y = temp, color = humid)
  ) + geom_point()
```

5. Saving plot to project:

```{r}
ggsave("temp_humid_hour.pdf")
```


