---
title: "Homework 1"
author: "Wenxin Tian"
date: "`r Sys.Date()`"
output: github_document
---

## Problem 1:

1. Importing data:

```{r, echo = FALSE, message = FALSE}
library(moderndive)
library(tidyverse)
```

```{r}
data("early_january_weather")
```

2. A glimpse at the data:

```{r}
head(early_january_weather)
```


3. Short description of the data:

The imported data consists of weather conditions taken in early January in 2013. 
The variables include `r colnames(early_january_weather)`. The dataset has a size of 
`r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns, which means 
the data has `r ncol(early_january_weather)` variables taken across `r nrow(early_january_weather)`
 different timepoints. Across all the timepoints, the main temperature was `r round(mean(pull(early_january_weather, temp)), digits = 2)`
  degrees.
  
4. Scatter plot showing temperature and humidity across different hours:

```{r}
ggplot(
  early_january_weather, 
  aes(x = time_hour, y = temp, color = humid)
  ) + geom_point()
```

5. Saving plot to project:

```{r}
ggsave("temp_humid_hour.pdf")
```

## Problem 2:

1. Creating practice dataframe:

```{r}
df = tibble(
  norm_samp = rnorm(n = 10, mean = 0, sd = 1),
  norm_samp_pos = norm_samp > 0,
  char_vec = c('a', 'b', 'c', 'd', 'e', 'f', 'g', 'h', 'i', 'j'),
  fac_vec = factor(sample(c('Green', 'Red', 'Blue'), 10, replace = TRUE))
)
```
2. Taking means of each variable:

```{r}
norm_samp_mean = mean(pull(df, norm_samp))
norm_samp_pos_mean = mean(pull(df, norm_samp_pos))
char_vec_mean = mean(pull(df, char_vec))
fac_vec_mean = mean(pull(df, fac_vec))
```

For random numbers from the normal distribution, a numeric mean was taken. For logical values, 
they were treated as 0's and 1's, and a mean was taken. For character vector and factor vector, 
the `mean` function returned `NA`, as they are not numeric values.

3. Applying `as.numeric` to variables:

```{r, message = FALSE, results = 'hide'}
as.numeric(pull(df, norm_samp_pos))
as.numeric(pull(df, char_vec))
as.numeric(pull(df, fac_vec))
```

When trying to apply `as.numeric()` to the variables, logical values were converted to 1's and 0's, 
character vector returned `NA`s because of coercion, and factor vector returned its levels. This result
 is consistent with what happened when I tried to take the means, since only the logical values could be 
 converted to numeric values. However, I was surprised that even though `as.numeric()` returned levels 
 of the factor vector, taking its mean still returned `NA`.
